Fast Sorting on Modern Computers

### 2005-07-30 docs/tech_report/method.tex
minor changes to references

\section{Testing details}
%TODO a lot of this may be in the first sorts chapter, maybe heapsort.
discuss: BIG + random.org, 64 bit in lamarca vs 32 bit, do_nothing and how it
affects cache hits, scaling in the software branch predictors. How to compare
and contrast varying results (branch vs softwre branhc; P4 vs simplescalar).
What factors are used for testing: /proc/cpuinfo output, cahce and branch
predictor data from P4, simplescalar inputs, software predictor, verfication of
sorts.

>>>>

\section{Testing details}

%TODO a lot of this may be in the first sorts chapter, maybe heapsort.
%discuss: BIG + random.org, 64 bit in lamarca vs 32 bit, do_nothing and how it
%affects cache hits, scaling in the software branch predictors. How to compare
%and contrast varying results (branch vs softwre branhc; P4 vs simplescalar).
%What factors are used for testing: /proc/cpuinfo output, cahce and branch
%predictor data from P4, simplescalar inputs, software predictor, verfication of
%sorts.

### 2005-07-30 docs/tech_report/shell.tex
minor changes to references

Shellsort's simulation results have the characterist shape and range of an
$O(NlogN)$ sort, albeit, not a very good one. The slopes of its graphs are
slighlty steeper, as can be seen in Figures \ref{shell cycles}, \ref{shell
instruction count}, \ref{shell level 1 misses} and \ref{shell branch
mispredictions}. It performs better than a
heapsort, but considerably worse than quicksort. However, it easier to program
than either of these two sort.

@@

Improved shellsort does improve on shellsort, having approximately 10\% fewer
instructions. It also has slightly fewer cache misses and branch mispredictions.
Overall, this leads to a reduction in cycle count of between 35 and 70\%, as
seen in Figure \ref{shell cycle count}.

>>>>

Shellsort's simulation results have the characterist shape and range of an
$O(NlogN)$ sort, albeit, not a very good one. The slopes of its graphs are
slighlty steeper, as can be seen in Figures \ref{shell cycles}, \ref{shell
instructions}, \ref{shell level 1 misses} and \ref{shell branch
misses}. It performs better than a
heapsort, but considerably worse than quicksort. However, it easier to program
than either of these two sort.

@@

Improved shellsort does improve on shellsort, having approximately 10\% fewer
instructions. It also has slightly fewer cache misses and branch mispredictions.
Overall, this leads to a reduction in cycle count of between 35 and 70\%, as
seen in Figure \ref{shell cycles}.
